Poseidon Adventure

### 2019-06-15 FullBoccaccioTruthEx2.Rmd
add bocaccio example; age splitting needs more work

After corrections were applied to `calc_Z` we were closer to the ballpark in NOBA. This demonstrates that the estimated true ages are not working between the cohort ages, they just drop to 0. This is consistent with what we observed for NOBA. The numbers at true age [don't match atlantis output where we have it for NOBA](https://sgaichas.github.io/poseidon-dev/TestCalcZ.html), so I will do further testing with this function and `calc_stage2age`.

@@

@@

This is true catch at age for bocaccio (in age classes, not true ages):

@@

```{r cattrueage}

@@

@@

```{r userset-maxlen, echo=TRUE}

@@

>>>>

After corrections were applied to `calc_Z` we were closer to the ballpark in NOBA. While the estimated true ages no longer just drop to 0, the patterns here don't seem like a good enough approximation of how age class would decay. The numbers at true age for NOBA cod are closer because there are only 2 ages within a stage to split, but they still [don't match atlantis output where we have it for NOBA](https://sgaichas.github.io/poseidon-dev/TestCalcZ.html), so I will do further testing with this `calc_Z` and `calc_stage2age`.

@@

We may need to rethink the annual Z we are estimating to do the approximation.

@@

This is true catch at (st)age for bocaccio (in age classes, not true ages):

@@

```{r cattrueage, warning=FALSE, message=FALSE}

@@

These still don't look quite right.

@@

```{r userset-maxlen, echo=TRUE, eval=FALSE}

@@

saveRDS(catch_length_census_ss, file.path(d.name, paste0(scenario.name, "catchlength_census_sardhakeboca.rds")))

### 2019-06-15 docs/index.Rmd
add bocaccio example; age splitting needs more work

>>>>

June 15: while the age splitting is functioning better, applying it to a species with more than 2 ages per age class (CC Bocaccio rockfish) shows that our application of an annual Z estimate may not be the best approach. The functions themselves could use further tweaking.

Overall it is advisable to use true age output from more recent Atlantis codebases where possible.

<a href="https://sgaichas.github.io/poseidon-dev/FullBoccaccioTruthEx2.html" target="_blank">Redo Bocaccio test with CCA F scenario, June 15, 2019</a>
